\section*{Evaluation Metrics in Linguistic Steganography}

This section outlines the key metrics used to evaluate the effectiveness and performance of linguistic steganography techniques.

\subsection*{5.1 Imperceptibility Metrics}

Placeholder paragraph for imperceptibility metrics.

\subsubsection*{5.1.1 Perceptual-Imperceptibility (Text Quality)}

Placeholder paragraph for perceptual-imperceptibility.

\paragraph*{Perplexity (PPL)}

Placeholder paragraph for Perplexity (PPL).

\paragraph*{Distinct-n, MAUVE}

Placeholder paragraph for Distinct-n, MAUVE.

\paragraph*{Human Evaluation}

Placeholder paragraph for Human Evaluation.

\subsubsection*{5.1.2 Statistical-Imperceptibility (Inseparability)}

Placeholder paragraph for statistical-imperceptibility.

\paragraph*{Kullback-Leibler Divergence (KLD)}

Placeholder paragraph for Kullback-Leibler Divergence (KLD).

\paragraph*{Jensen-Shannon Divergence (JSD)}

Placeholder paragraph for Jensen-Shannon Divergence (JSD).

\paragraph*{Anti-Steganalysis Accuracy (ACC)}

Placeholder paragraph for Anti-Steganalysis Accuracy (ACC).

\paragraph*{Mean and Variance (of masked word positions)}

Placeholder paragraph for Mean and Variance (of masked word positions).

\paragraph*{Semantic Similarity (SS)}

Placeholder paragraph for Semantic Similarity (SS).

\subsection*{5.2 Embedding Capacity Metrics}

Placeholder paragraph for embedding capacity metrics.

\paragraph*{Bits per Token (BPT) / Bits per Word (BPW) / Embedding Rate (ER)}

Placeholder paragraph for Bits per Token (BPT) / Bits per Word (BPW) / Embedding Rate (ER).